---
title: "formbuildr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{formbuildr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The package `formbuildr` was designed to readily create forms using the R console or a plain text file. A form is made of a series of questions and post-processing functions combined. 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(formbuildr)
```




# Create a form with R console 

## Questions


```{R q1}
q1 <- fob_int("How old are you?")
class(q1)
```

Various questions with answers of pre-determined types are already implemented. 

```R
R> q1()                                                            
❓ How old are you?
Enter your answer (an integer): 10                                 
✔ validated!
[1] 10
```

In interactive mode, validation are done interactively.

```R
R> q1()                                                            
❓ How old are you?
Enter your answer (an integer): 10.1                               
⚠ Validation failed, try again!
Enter your answer (an integer): 10                                 
✔ validated!
[1] 10
```








## Combining questions

## Post-processing 

<!-- depending on the function, is automatically validated. -->


# Create a form from a plain text


# Example 